### 2015-08-11 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Update README files and Manual AxiSEM + clean coupling UTILS

@@

\item[\textbullet] ATTENUATION         false
\item[\textbullet] SAVE\_SNAPSHOTS     true

@@

\noindent {\color{red} NOTE:} If you already know the value of the begin time and if it is already configured in 'reformat.par', you can launch the compilation of expand\_2D\_3D and reformat, AND the execution of this two programs with the single script :

@@

@@

\section{STEP ? : Set up scripts}

>>>>

\noindent In Axisem directory, there are all the parameter files, scripts, stations, etc., to put in Axisem mesher and solver directories, for each example, here:

\noindent {\small 'utils/EXTERNAL\_CODES\_coupled\_with\_SPECFEM3D/AxiSEM\_for\_SPECFEM3D/Parfiles\_and\_scripts\_for\_examples'}

\noindent Cf 'README' in this directory for more details.

@@

\item[\textbullet] MESHNAME            ~~ NAME\_OF\_DESTINATION\_MESH\_DIR
\item[\textbullet] ATTENUATION         ~~ false
\item[\textbullet] SAVE\_SNAPSHOTS     ~~ true

@@

\noindent {\color{red} NOTE:} If you already know the value of the begin time and if it is already configured in 'reformat.par', you can launch the compilation of expand\_2D\_3D and reformat, AND the execution of this two programs with the single script (AND uncomment the LAST LINE of the script 'sub\_called\_batch\_for\_expand2D3D\_Curie\_CD.sh' BEFORE that) :

@@

\noindent !! CAUTION : don't forget to UNCOMMENT the last line

\noindent (\#\#\#\#ccc\_msub -q standard ../sub\_called\_batch\_for\_reformat\_Curie\_CD.sh)

\noindent of 'sub\_called\_batch\_for\_expand2D3D\_Curie\_CD.sh', which will launch the reformat script at the end !!

@@

%%\section{STEP ? : Set up scripts}
